### 2014-12-02 writing/F'14 paper/sick.tex
Paper update; mat file loading.

The tree-pair model architecture that we use is novel, and though the underlying recursive approach has been validated elsewhere, there is no guarantee that this architecture is suitable for handling inference over real natural language. To ensure that this is the case, we also train a version of our model on an existing competition dataset, the ICK textual entailment challenge \cite{marelli2014sick}. The corpus consists of about 10k natural language sentence pairs (generated using data expansion from a smaller set), labeled with \ii{entailment}, \ii{contradiction}, or \ii{neutral}. At only a few thousand distinct sentences (many of them variants on an even smaller set of template sentences), the corpus is not large enough to train a high quality learned model of general natural language, but it is the largest hand labeled entailment corpus that we are aware of.

@@

We initialized our word embeddings using the TODO dimensional vectors provided with 
GloVe \cite{pennington2014glove}. Before any embedding is used as an input to a recursive layer, 
it is passed through an additional $\tanh$ neural network layer that transforms
the embedding from the embedding dimension to the dimension of the recursive layer.

We supplemented the roughly 5000 SICK training examples\footnote{We tuned the model using performance on a held out development set, but report performance here for a version of the model trained on both the training and development data and tested on the SICK test set.} with TODO examples of approximate entailment data from the Denotation Graph project \cite{hodoshimage}. We parsed all data with the Stanford PCFG Parser v. 3.3.1 \cite{klein2003accurate}. To accelerate convergence, we collapsed subtrees that were identical across both sentences in a pair down to a single head word. In order to improve regularization on the noisier data, we used dropout \cite{hinton2012improving} at the input to the comparison layer (10\%) and at the output from the embedding transform layer (25\%). We trained a single model on data from both sources, but used a separate set of softmax parameters for classifying into the labels from each source.

>>>>

The tree-pair model architecture that we use is novel, and though the underlying recursive approach has been validated elsewhere, there is no guarantee that this architecture is suitable for handling inference in the face of the noisy labels and diverse range of linguistic structures seen in typical natural language data. To ensure that this is the case, we also train a version of our model on an existing competition dataset, the SICK textual entailment challenge \cite{marelli2014sick}. The corpus consists of about 10k natural language sentence pairs (generated using data expansion from a smaller set), labeled with \ii{entailment}, \ii{contradiction}, or \ii{neutral}. At only a few thousand distinct sentences (many of them variants on an even smaller set of template sentences), the corpus is not large enough to train a high quality learned model of general natural language, but it is the largest hand labeled entailment corpus that we are aware of.

@@

Adapting to this task required us to make a few additions to the techniques discussed in Section \ref{methods}. In order to better handle rare words, we initialized our word embeddings using the 200 dimensional vectors trained with 
GloVe \cite{pennington2014glove} on data from Wikipedia. Since 200 dimensional vectors are too large to be practical in an RNTN, especially on a small dataset, a new embedding transformation layer is needed. Before any embedding is used as an input to a recursive layer, it is passed through an additional $\tanh$ neural network layer with the same output dimension as the recursive layer.

We also supplemented the SICK training data\footnote{We tuned the model using performance on a held out development set, but report performance here for a version of the model trained on both the training and development data and tested on the SICK test set.} with TODO examples of entailment data from the Denotation Graph project \cite{hodoshimage}, a corpus of automatically labeled (and thus noisy) entailment examples over image captions, the same genre of text from which SICK was drawn. We trained a single model on data from both sources, but used a separate set of softmax parameters for classifying into the labels from each source. We parsed the data from both sources with the Stanford PCFG Parser v. 3.3.1 \cite{klein2003accurate}. We also found that we were able to train a working model much more quickly with an additional technique: we collapse subtrees that were identical across both sentences in a pair down to a single head word. Finally, in order to improve regularization on the noisier data, we used dropout \cite{hinton2012improving} at the input to the comparison layer (10\%) and at the output from the embedding transform layer (25\%).
